\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{hyperref} % Include the hyperref package
\usepackage{fontawesome}
\usepackage[left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry}

% Adjust the section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{0.5em}{0.25em}

\titleformat{\subsection}{\bfseries}{}{0em}{}
\titlespacing{\subsection}{0pt}{0.25em}{0.1em}

\begin{document}

\pagestyle{empty}

\begin{center}
    {\LARGE \textbf{Mallikarjun R Wali}} \\
    \vspace{0.1cm}
    \href{mailto:walimallikarjun275@gmail.com}{walimallikarjun275@gmail.com} $\cdot$ +91-9353916915 $\cdot$ Bangalore \\
    \vspace{0.1cm}
    \href{https://www.linkedin.com/in/mallikarjun-r-wali-29768722b}{ \faLinkedin } $\cdot$ \href{https://leetcode.com/Mallikarjun_W/}{Leetcode} $\cdot$ \href{https://github.com/Mallikarjun9353/}{\faGithub} $\cdot$ 
    \href{https://www.hackerrank.com/profile/walimallikarjun2}{Hackerrank} $\cdot$ 
    \href{https://www.codingninjas.com/studio/profile/Wali}{CodingNinjas} \\
\end{center}

\section*{Education}
\noindent\textbf{Acharya Institute of Technology, Bangalore} \hfill Aug 2019 -- May 2023 \\
\noindent\textit{BE-CSE} \hfill 8.53 CGPA

\noindent\textbf{Alvas PU College, DK} \hfill Jun 2017 -- May 2019 \\
\noindent\textit{PUC- [12th]} \hfill 94.16\% 

\noindent\textbf{Sant Meera English Medium School, Belagavi} \hfill Jun 2016 -- Apr 2017 \\
\noindent\textit{SSLC- [10th]} \hfill 89.60\% 

\section*{Experience}
\noindent\textbf{Associate Software Engineer }\href{https://www.cgi.com/en}{\faLink} \hfill July 2024 -- Present \\
\noindent\textit{CGI, Bangalore} 
\begin{itemize}[leftmargin=0.15in]
    \setlength{\itemsep}{0.05em} % Reduce space between items
    \setlength{\parskip}{0em}    % Reduce space between paragraphs within items
    \item Designed \textbf{CI/CD} pipelines using \textbf{Gitlab}, \textbf{Jenkins}, and automation tools to streamline deployments.
    \item Managed containers using \textbf{Docker, Kubernetes}, and \textbf{Openshift} for efficient scaling and reliability.
    \item Optimized Linux-based servers and collaborated with teams to enhance DevOps workflows.
\end{itemize}



\noindent\textbf{Software Engineer Intern}\href{https://7-elevengsc.com/}{\faLink} \hfill Oct 2023 -- Apr 2024 \\
\noindent\textit{7-Eleven GSC,Bangalore} 

\begin{itemize}[leftmargin=0.15in]
    \setlength{\itemsep}{0.05em} % Reduce space between items
    \setlength{\parskip}{0em}    % Reduce space between paragraphs within items
    \item Developed and optimized \textbf{microservices} and \textbf{REST APIs} with \textbf{Java} and \textbf{SpringBoot}.
       \item Performed API testing with \textbf{POSTMAN} and validated microservices using \textbf{JUnit}.
    \item Utilized \textbf{SQL} for efficient database operations.
    \item Optimized \textbf{Python} code to improve performance and efficiency. 
\end{itemize}

\section*{Projects}
\noindent\textbf{IDS using Machine Learning Algorithms}\href{https://github.com/Mallikarjun9353/}{Website} \hfill  \\
\noindent\textit{Python, ML} 
\begin{itemize}[leftmargin=0.15in]
    \setlength{\itemsep}{0.05em} % Reduce space between items
    \setlength{\parskip}{0em}    % Reduce space between paragraphs within items
    \item Main Objective of this project is to find out if the website is being intruded upon.
    \item Feature engineering and EDA using \textbf{Jupyter Notebook}, \textbf{Numpy}, \textbf{Pandas}, and \textbf{visualization} libraries.
    \item Used various \textbf{machine learning models} to detect and classify threats.
    \item \textbf{Tech Stack: Python, Flask, Machine Learning}
\end{itemize}
\\
\\
\noindent\textbf{TaskGuard Application} \hfill \\
\noindent\textit{Python, Flask}
\begin{itemize}[leftmargin=0.15in, itemsep=0.1em]
    \setlength{\itemsep}{0.05em} % Reduce space between items
    \setlength{\parskip}{0em}    % Reduce space between paragraphs within items
    \item Developed secure user login/signup with password encryption.
    \item Implemented to-do list feature for adding and deleting tasks.
    \item Utilized \textbf{Python} and \textbf{Flask} for backend, \textbf{SQLAlchemy} for database management.
    \item Ensured secure user authentication with encrypted passwords.
\end{itemize}

\section*{Technical Skills}
\begin{itemize}[leftmargin=0.15in, itemsep=0.1em]
    \item \textbf{Languages:} Python, Java, C++.
    \item \textbf{General:} Data Structures and Algorithms, Object-Oriented Programming.
    \item \textbf{Developer Tools:} Postman, VS Code, Jupyter Notebook, IntelliJ, Pycharm.
    \item \textbf{Technologies:} Rest APIs, Machine Learning, Git.
    \item \textbf{Database:} SQL, PostgreSQL, MongoDB.
    \item \textbf{Frameworks/Libraries:} Flask, JUnit, Numpy, Pandas.
\end{itemize}

\section*{Additional Achievement}
\begin{itemize}[leftmargin=0.15in, itemsep=0.1em]
    \item \textbf{HackerRank:} Max Rating - 4 Star (Python), 3 Star (SQL) \href{https://www.hackerrank.com/profile/walimallikarjun2}{[HackerRank]}
    \item Solved 200+ Competitive programming and DSA problems on various coding platforms.
    \item \href{https://leetcode.com/Mallikarjun_W/}{Leetcode}, \href{https://www.codingninjas.com/studio/profile/Wali}{Coding Ninjas}, \href{https://www.hackerrank.com/profile/walimallikarjun2}{HackerRank}
\end{itemize}

\end{document}